\cvsection{Research Experience}
\begin{cventries}
  \cventry
    {Master Thesis}
    {The Influence of Temporal Leadership on Employees 'job crafting: Based on Resource Conservation Theory}
    {Lanzhou, China}
    {Sep. 2017 - Now}
    {
      \begin{cvitems}
        \item {Abstract: Thesis content: This research is based on theory of resource conservation and uses time pressure, time attitude and work passion as media ting variables to explore the relationship between temporal leadership and employees’ job crafting behavior and its internal mechanism of action from a temporal perspective.}
      \end{cvitems}
     }
  \cventry
    {IACMR Conference presentation paper}
    {Can Similarity Bring More Voice? An Investigation of The Relationship Between Relational Demography and Subordinates' Voice Behavior}
    {Wuhan, China}
    {Jun. 2017}
    {
      \begin{cvitems}
        \item {\url{https://github.com/JaggerWu/weed-recognization}}
        \item {Abstract: Based on similarity–attraction paradigm and social identity theory, this article investigated the relationship between relational demography and subordinates' voice behavior, and the mediating effect of voice self-efficacy and voice psychological safety.}
      \end{cvitems}
     }
  \cventry
    {Bachelor Thesis}
    {The job prospects of low-skilled workers}
    {Lanzhou, China}
    {Sep. 2014 - Jun. 2015}
    {
      \begin{cvitems}
      \item {Abstract: The case study was mainly conducted on the career planning plan of security guards at the Lanzhou D brand clothing apparel square. Based on internal motivation theory, professional tendency theory，It provides programs for the career design of low-skilled employees, and suggests ways for companies to retain low-skilled employees and increase their loyalty to the company.}
      \end{cvitems}
    }
  \cventry
    {Success Plan of school of management}
    {Research on the Relationship between Work Motivation and Emotional Labor Strategy of Front-line Employees}
    {Lanzhou, China}
    {Apr. 2013 - Nov. 2013}
    {
      \begin{cvitems}
        \item {The article tries to answer what kind of relationship between front-line service employees' motivation for work and the emotional work strategies they use?}
      \end{cvitems} 
    }
\end{cventries}
